Write an R program to create three vectors a, b, c with 5 integers. Combine the three vectors to become a 3×5 matrix where each column represents a vector. Print the content of the matrix. Plot a graph and label correctly.

```{r}
my_vec1 <- c(8,6,7,8,4)
my_vec2 <- c(5,1,2,3,1)
my_vec3 <- c(9,7,3,2,6)
add_vec=my_vec1+my_vec2+my_vec3
print(add_vec)
data <- c(my_vec1,my_vec2,my_vec3)
my_matrix <- matrix(data,nrow=3, c(ncol=5))
my_matrix

my_matrix2 <- cbind(my_vec1,my_vec2,my_vec3)
my_matrix2
plot(my_matrix2, type ="b", col="blue", pch=1)
?plot
```
Write a R program to create a Data frames which contain details of 5 employees and display the details.(Name, Age,Role and Length of service). 
```{r}
Name <- c("Aadhav","Daisy","Stephen","Matthew","David")
Age <- c(25,32,38,31,49)
Role <- c("Data Scientist","Data Analyst","Data Architect","Data Engineer","Data Governor")
Length_of_service <- c(5,8,9,6,10)
frame <- data.frame(Name,Age,Role,Length_of_service)
frame
```
Import the GGPLOT 2 library and plot a graph using the qplot function. X axis is the sequence of 1:20 and the y axis is the x ^ 2. Label the graph appropriately. install.packages("ggplot2",dependencies = TRUE)



```{r}
library(ggplot2)
x <- seq(1:20)
y <- x^2
frame1 <- data.frame(x,y)

qplot(x,y)
# Add line
qplot(x, y, geom=c("point", "line"))


#qplot(frame1 = x, y , geom = "bar")

ggplot(frame1, aes(x, y)) + geom_jitter(position = position_jitter(0.5),aes(colour = x),cex = 1.8, shape = 8)
                
```



Create a simple bar plot of five subjects.
```{r}

Subjects <- c("English","Maths","History","Physics","Chemistry")
Marks <- c(80,90,45,77,68) 
frame3 <- data.frame(Subjects,Marks)
frame3
barplot(Marks,
        main ="Marks",
        xlab="Subjects",ylab="Marks",
        )
```
Write a R program to take input from the user (name and age) and display the values. 


```{r}
Name <- readline("Enter your name: ")
Age <- readline("Enter your age: ")
data1 <- paste("Your name is ",Name,"and your age is ", Age)
data1
```


Write a R program to create a sequence of numbers from 20 to 50 and find the mean of numbers from 20 to 50 and sum of numbers.

```{r}
prog <- seq(20:50)
prog
mean1 <- mean(prog)
sum1 <- sum(prog)
mean1
sum1
```

Write a R program to create a vector which contains 10 random integer values between -50 and +50


```{r}
data <- runif(10, min=-50, max=50)
data
```

Write a R program to get the first 10 Fibonacci 
numbers
```{r}
x = 0
y = 1
count = 1
target = 11
print("Fibonacci sequence:")
print(x)
print(y)
while(count < target)
{
n = x + y
print(n)
x = y
y = n
count = count + 1
}

```
Write a R program to print the numbers from 1 to 100 
and print "Fizz" for multiples of 3, print "Buzz" for 
multiples of 5, and print "FizzBuzz" for multiples of 
both




```{r}
n=1
for (n in c(1:100))
{
#print(n)
if
  (n%%3 == 0 && n%%5 == 0)
  {
    print("fizzbuzz")
  }  
else if(n%%5 == 0)
 {
    print("buzz")
  }
  
else if(n%%3 == 0)
  {
    print("Fizz")
  }


else
  {
    print(n)
  }
}
```

